Modeling the impacts of replacing car trips with combined public transport and cycling: \ Reproducible methods, results and actionable evidence from the biclaR project

### 2023-11-29 paper/PaperCEUS/PaperCEUS.Rmd

The quantification of benefits can support policy-makers in prioritizing interventions to reduce the reliance on individual motorized transportation.
The presentation of the results in an open access web application will help  communicate decisions.
Furthermore, the provision of datasets resulting from this project provides a foundation for further research and development of new tools and methods.

@@

We used open-source tools and transparent methods.
By making the research process publicly accessible in a code repository (see [Research Data](#research-data)), it enables the replication of similar estimates for socio-environmental impacts, resulting from a modal shift from car to bicycle in combination with PT, in other metropolitan areas.

>>>>

The quantification of benefits can support policy-makers in prioritizing interventions to reduce the reliance on individual motorized transportation.
The presentation of the results in an open access web application will help  communicate decisions.
Furthermore, the provision of datasets resulting from this project provides a foundation for further research and development of new tools and methods.
<!-- Punchy final sentence: -->
The methods are reproducible and based on open source software, which can be applied to other cities and metropolitan areas, supporting the decarbonization of transport systems internationally.

@@

<!-- We used open-source tools and transparent methods.
By making the research process publicly accessible in a code repository (see [Research Data](#research-data)), it enables the replication of similar estimates for socio-environmental impacts, resulting from a modal shift from car to bicycle in combination with PT, in other metropolitan areas. -->
